Paper 1

### 2022-06-16 scripts/Paper 1.Rmd
boring x axis

@@

input.rearranged$season <- "" # add season variable

@@

(SWC.20 <- input.rearranged %>% filter (GSYear == "19/20"| GSYear == "20/21" | GSYear == "21/22" ) %>% ggplot(., aes(x = as.Date(dayssinceJul1, origin = as.Date("07-01", "%m-%d")), SWC, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1.5)+
  # scale_x_continuous(limits = c(0, 365))+
  xlab('Month') +
  ylab('SWC %') +
   scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("07-01", "06-31"), "%m-%d"))+
    scale_color_manual(values = group.colors)+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

SWC.20
tiff("SWC22.tiff", units="in", width=10, height=6,  res=300)
print(SWC.20)
dev.off()
```

```{r, fig.width = 10, fig.height = 6}
Legend.met<- get_legend(SP.rain+ theme(legend.position = 'right'))

Fig1 <- plot_grid(rainfall.p + theme(legend.position="none"), TA+ theme(legend.position="none"),
             SWC.20+ theme(legend.position="none"), TS+ theme(legend.position="none"), ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))

Fig1
tiff("Fig1.tiff", units="in", width=10, height=6,  res=300)
print(Fig1)
dev.off()

Legend.met
```

@@

```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))

GPP.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))

ER.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(ER_LT.gC))

Ts.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.mean = mean(Ts.mean))

# check when switches from sink to source

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
         scale_x_discrete(limits = month.abb) +

  ylab("Monthly NEE")+
  xlab("month")+
  theme_classic()

GPP.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly GPP")+
  xlab("month")+
  theme_classic()

ER.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()

Ts.summary %>%
  ggplot(., aes(x = month, y = monthly.mean, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()
```

@@

(NEEcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(dayssinceJul1, NEEcum, color = GSYear)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
  xlab("Days since July 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

(NEE.time <- input.daily %>% 
  ggplot(., aes(jday, NEE_LT.gC, color = Year)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative NEE (g C' ~m^-2~ day^-1*')'))+
  xlab("Days since July 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

(NEE.bar <- NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
         scale_x_discrete(limits = month.abb) +
  ylab(bquote('Total monthly NEE (g C' ~m^-2~')'))+
  xlab("Month")+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

(GPPcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(dayssinceJul1, GPPcum, color = GSYear)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
  xlab("Days since July 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

@@

```{r}
(GPPcum.p <-cum.co2fluxes %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = cumsum(GPP_LT.gC)) %>%
   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
  geom_col() + 
  ylab("Total GPP")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

(ERcum.p <-cum.co2fluxes %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = cumsum(ER_LT.gC)) %>%
   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
  geom_col() + 
  ylab("Total ER")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))
```

```{r, fig.height=10, fig.width = 6}

(Fig3 <- plot_grid(rain,
             GPPcum.p, ERcum.p, nrow =3))

>>>>

```{r}
input.daily$dayssinceJun1 <- ""

Grow19.20 <- input.daily[1:164,]
Grow19.20$dayssinceJun1 <- 202:365
Grow19.20$GSYear <- "19/20"

Grow20.21 <- input.daily[165:529,]
Grow20.21$dayssinceJun1 <- 1:365
Grow20.21$GSYear <- "20/21"

Grow21.22 <- input.daily[530:907,]
Grow21.22$dayssinceJun1 <-1:378
Grow21.22$GSYear <- "21/22"

start.time <- as.Date("06-01", "%m-%d")
end.time <- as.Date("06-30", "%m-%d")
start.end <- c(start.time, end.time)
```

@@

@@

(SWC.20 <- input.rearranged %>% filter (GSYear == "19/20" ) %>% ggplot(., aes(x = as.Date(dayssinceJun1, origin = as.Date("06-01", "%m-%d")), SWC, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1.5)+
  # scale_x_continuous(limits = c(0, 365))+
  xlab('Month') +
  ylab('SWC %') +
   scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("06-01", "05-31"), "%m-%d"))+
    scale_color_manual(values = group.colors)+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

SWC.20
tiff("SWC20.tiff", units="in", width=10, height=6,  res=300)
print(SWC.20)
dev.off()
```

@@

```{r seasonal NEE}
NEE.summary <- input.rearranged %>% ddply(c("GSYear", "month.name"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))
NEE.summary$month.name <- factor(NEE.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))

(NEE.bar <- NEE.summary  %>%
  ggplot(., aes(x = month.name, y = monthly.sum, group = GSYear, fill = GSYear)) +
  geom_col(position = "dodge", aes(fill = GSYear)) + 
         #scale_x_discrete(limits = start.end)+
  ylab("Monthly NEE")+
  xlab("month")+
  theme_classic())

NEE.bar
tiff("NEEbar.tiff", units="in", width=10, height=6,  res=300)
print(NEE.bar)
dev.off()
```

```{r}
GPP.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))
#GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))

(GPP.bar <- GPP.summary  %>%
  ggplot(., aes(x = season, y = monthly.sum, group = GSYear, fill = GSYear)) +
  geom_col(position = "dodge", aes(fill = GSYear)) + 
         #scale_x_discrete(limits = start.end)+
  ylab("Monthly GPP")+
  xlab("month")+
  theme_classic())
```

```{r}
ER.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
                                       monthly.sum = sum(ER_LT.gC))
#ER.summary$month.name <- factor(ER.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))

(ER.bar <- ER.summary  %>%
  ggplot(., aes(x = season, y = monthly.sum, group = GSYear, fill = GSYear)) +
  geom_col(position = "dodge", aes(fill = GSYear)) + 
         #scale_x_discrete(limits = start.end)+
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic())
```

@@

(NEEcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(x = as.Date(dayssinceJul1, origin = as.Date("07-01", "%m-%d")), NEEcum, color = GSYear)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
  xlab("Days since July 1st")+
       scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("07-01", "06-31"), "%m-%d"))+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

NEEcum.p
tiff("NEEcum.tiff", units="in", width=10, height=6,  res=300)
print(NEEcum.p)
dev.off()

(GPPcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(dayssinceJul1, GPPcum, color = GSYear)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative GPP (g C ' ~m^-2~')'))+
  xlab("Days since July 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

@@

```{r}
(GPPcum.p <-cum.co2fluxes %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = cumsum(GPP_LT.gC)) %>% filter(season == "Winter") %>%
   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
  geom_col() + 
  ylab("Total GPP")+
  xlab("Growing season year")+
   scale_y_continuous(limits = c(0,60000))+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

GPPcum.p
tiff("GPP.tiff", units="in", width=10, height=6,  res=300)
print(GPPcum.p)
dev.off()

(ERcum.p <-cum.co2fluxes %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = cumsum(ER_LT.gC)) %>% filter(season == "Summer") %>%
   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
  geom_col() + 
       scale_y_continuous(limits = c(0,60000))+
  ylab("Total ER")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

ERcum.p
tiff("ER.tiff", units="in", width=10, height=6,  res=300)
print(ERcum.p)
dev.off()
```
